---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# chktemplate

<!-- badges: start -->
[![R build status](https://github.com/poissonconsulting/chktemplate/workflows/R-CMD-check/badge.svg)](https://github.com/poissonconsulting/chktemplate/actions)
[![codecov](https://codecov.io/gh/poissonconsulting/chktemplate/branch/master/graph/badge.svg?token=FR6YQNTZF3)](https://codecov.io/gh/poissonconsulting/chktemplate)
<!-- badges: end -->

Modify a `shinyupload` template to human-readable format.

## Installation

You can install the development version from [GitHub](https://github.com/poissonconsulting/chktemplate) with:

``` r
# install.packages("remotes")
remotes::install_github("poissonconsulting/chktemplate")
```

## Demonstration

`chktemplate` is an R package of utility functions. 
It is designed to be used in conjunction with the `shinyupload2` package.

Consider the demonstration template - each data frame is converted into human readable format using the 
`template_human()` function.

```{r}
library(chktemplate)
library(tibble)
chktemplate::demo_template$outing
set.seed(42)
chktemplate::template_human(chktemplate::demo_template$outing)
```

## Code of Conduct

Please note that the `chktemplate` project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). 
By contributing to this project, you agree to abide by its terms.

