---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# chktemplate

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/poissonconsulting/chktemplate/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/chktemplate/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/chktemplate/branch/main/graph/badge.svg)](https://app.codecov.io/gh/poissonconsulting/chktemplate?branch=main)
<!-- badges: end -->

Work with a Shiny templates by turning them into human-readable format 
or confirm the data follows the template requirements.

## Installation

You can install the development version from [GitHub](https://github.com/poissonconsulting/chktemplate) with:

``` r
# install.packages("remotes")
remotes::install_github("poissonconsulting/chktemplate")
```

## Demonstration

### Convert Template to be Human Readable

First you can see how the template is written which is in a code based form, the code based form is then converted to be easily readable for humans. 
We will subset to the first four columns since there are too many columns to display on a single page.

```{r}
library(chktemplate)
chktemplate::demo_template_fish_exploit$outing[1:4]
chktemplate::template_human(chktemplate::demo_template_fish_exploit$outing[1:4])
```

### Check Data Against Template Requirements 

## Code of Conduct

Please note that the `chktemplate` project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). 
By contributing to this project, you agree to abide by its terms.
